When is Finding Little Graphs \\ Inside Big Graphs Hard?

### 2015-10-20 data-presentation-talk/talk.tex
A bit more
Tweaks

    \begin{center}\begin{tikzpicture}
        \node[draw, circle, fill=uofgcobalt, inner sep=4pt, font=\bfseries] (Na) at (1,  0) {1};
        \node[draw, circle, fill=uofgpumpkin, inner sep=4pt, font=\bfseries] (Nb) at (1, -1.5) {2};
        \node[draw, circle, fill=uofglawn, inner sep=4pt, font=\bfseries] (Nc) at (0, -3) {3};
        \node[draw, circle, fill=uofgthistle, inner sep=4pt, font=\bfseries] (Nd) at (2, -3) {4};

        \draw [ultra thick] (Na) -- (Nb);
        \draw [ultra thick] (Nb) -- (Nc);
        \draw [ultra thick] (Nc) -- (Nd);
        \draw [ultra thick] (Nb) -- (Nd);

        \node[draw, circle, fill=uofgcobalt, inner sep=4pt, font=\bfseries] (N1) at (5.5,  0) {1};
        \node[draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N2) at (7.5,  0) {2};
        \node[draw, circle, fill=uofgpumpkin, inner sep=4pt, font=\bfseries] (N3) at (5.5, -1.5) {3};
        \node[draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N4) at (7.5, -1.5) {4};
        \node[draw, circle, fill=uofglawn, inner sep=4pt, font=\bfseries] (N5) at (5.5, -3) {5};
        \node[draw, circle, fill=uofgthistle, inner sep=4pt, font=\bfseries] (N6) at (7.5, -3) {6};

        \draw [thick, color=uofgsandstone!50] (N1) -- (N2);
        \draw [ultra thick] (N1) -- (N3);
        \draw [thick, color=uofgsandstone!50] (N1) -- (N4);
        \draw [thick, color=uofgsandstone!50] (N2) -- (N4);
        \draw [ultra thick] (N3) -- (N5);
        \draw [ultra thick] (N3) -- (N6);
        \draw [thick, color=uofgsandstone!50] (N4) -- (N6);
        \draw [ultra thick] (N5) -- (N6);
        \draw [thick, color=uofgsandstone!50] (N2) to [in=45, out=315] (N6);
        \draw [thick, color=uofgsandstone!50] (N1) to [in=135, out=225] (N5);
    \end{tikzpicture}\end{center}

@@

    \begin{center}\begin{tikzpicture}
        \node[draw, circle, fill=uofgcobalt, inner sep=4pt, font=\bfseries] (Na) at (1,  0) {1};
        \node[draw, circle, fill=uofgpumpkin, inner sep=4pt, font=\bfseries] (Nb) at (1, -1.5) {2};
        \node[draw, circle, fill=uofglawn, inner sep=4pt, font=\bfseries] (Nc) at (0, -3) {3};
        \node[draw, circle, fill=uofgthistle, inner sep=4pt, font=\bfseries] (Nd) at (2, -3) {4};

        \draw [ultra thick] (Na) -- (Nb);
        \draw [ultra thick] (Nb) -- (Nc);
        \draw [ultra thick] (Nc) -- (Nd);
        \draw [ultra thick] (Nb) -- (Nd);

        \node[draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N1) at (5.5,  0) {1};
        \node[draw, circle, fill=uofgcobalt, inner sep=4pt, font=\bfseries] (N2) at (7.5,  0) {2};
        \node[draw, circle, fill=uofgthistle, inner sep=4pt, font=\bfseries] (N3) at (5.5, -1.5) {3};
        \node[draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N4) at (7.5, -1.5) {4};
        \node[draw, circle, fill=uofglawn, inner sep=4pt, font=\bfseries] (N5) at (5.5, -3) {5};
        \node[draw, circle, fill=uofgpumpkin, inner sep=4pt, font=\bfseries] (N6) at (7.5, -3) {6};

        \draw [thick, color=uofgsandstone!50] (N1) -- (N2);
        \draw [thick, color=uofgsandstone!50] (N1) -- (N3);
        \draw [thick, color=uofgsandstone!50] (N1) -- (N4);
        \draw [thick, color=uofgsandstone!50] (N2) -- (N4);
        \draw [ultra thick] (N3) -- (N5);
        \draw [ultra thick] (N3) -- (N6);
        \draw [thick, color=uofgsandstone!50] (N4) -- (N6);
        \draw [ultra thick] (N5) -- (N6);
        \draw [ultra thick] (N2) to [in=45, out=315] (N6);
        \draw [thick, color=uofgsandstone!50] (N1) to [in=135, out=225] (N5);

    \end{tikzpicture}\end{center}
\end{frame}

@@

\begin{frame}[t,plain]{What About Induced?}

@@

    \only<5>{
        \input{gen-graph-induced-2d-5}
    }

    \only<6>{
        \input{gen-graph-induced-3d-1}
    }

    \only<7>{
        \input{gen-graph-induced-3d-2}
    }

@@

>>>>

    \begin{center}\begin{tikzpicture}
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (Na) at (1,  0) {1};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (Nb) at (1, -1.5) {2};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (Nc) at (0, -3) {3};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (Nd) at (2, -3) {4};

        \node <2> [draw, circle, fill=uofgcobalt, inner sep=4pt, font=\bfseries] (Na) at (1,  0) {1};
        \node <2> [draw, circle, fill=uofgpumpkin, inner sep=4pt, font=\bfseries] (Nb) at (1, -1.5) {2};
        \node <2> [draw, circle, fill=uofglawn, inner sep=4pt, font=\bfseries] (Nc) at (0, -3) {3};
        \node <2> [draw, circle, fill=uofgthistle, inner sep=4pt, font=\bfseries] (Nd) at (2, -3) {4};

        \draw <1> [thick, color=uofgsandstone!50] (Na) -- (Nb);
        \draw <1> [thick, color=uofgsandstone!50] (Nb) -- (Nc);
        \draw <1> [thick, color=uofgsandstone!50] (Nc) -- (Nd);
        \draw <1> [thick, color=uofgsandstone!50] (Nb) -- (Nd);

        \draw <2> [ultra thick] (Na) -- (Nb);
        \draw <2> [ultra thick] (Nb) -- (Nc);
        \draw <2> [ultra thick] (Nc) -- (Nd);
        \draw <2> [ultra thick] (Nb) -- (Nd);

        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N1) at (5.5,  0) {1};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N2) at (7.5,  0) {2};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N3) at (5.5, -1.5) {3};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N4) at (7.5, -1.5) {4};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N5) at (5.5, -3) {5};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N6) at (7.5, -3) {6};

        \node <2> [draw, circle, fill=uofgcobalt, inner sep=4pt, font=\bfseries] (N1) at (5.5,  0) {1};
        \node <2> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N2) at (7.5,  0) {2};
        \node <2> [draw, circle, fill=uofgpumpkin, inner sep=4pt, font=\bfseries] (N3) at (5.5, -1.5) {3};
        \node <2> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N4) at (7.5, -1.5) {4};
        \node <2> [draw, circle, fill=uofglawn, inner sep=4pt, font=\bfseries] (N5) at (5.5, -3) {5};
        \node <2> [draw, circle, fill=uofgthistle, inner sep=4pt, font=\bfseries] (N6) at (7.5, -3) {6};

        \draw <1> [thick, color=uofgsandstone!50] (N1) -- (N2);
        \draw <1> [thick, color=uofgsandstone!50] (N1) -- (N3);
        \draw <1> [thick, color=uofgsandstone!50] (N1) -- (N4);
        \draw <1> [thick, color=uofgsandstone!50] (N2) -- (N4);
        \draw <1> [thick, color=uofgsandstone!50] (N3) -- (N5);
        \draw <1> [thick, color=uofgsandstone!50] (N3) -- (N6);
        \draw <1> [thick, color=uofgsandstone!50] (N4) -- (N6);
        \draw <1> [thick, color=uofgsandstone!50] (N5) -- (N6);
        \draw <1> [thick, color=uofgsandstone!50] (N2) to [in=45, out=315] (N6);
        \draw <1> [thick, color=uofgsandstone!50] (N1) to [in=135, out=225] (N5);

        \draw <2> [thick, color=uofgsandstone!50] (N1) -- (N2);
        \draw <2> [ultra thick] (N1) -- (N3);
        \draw <2> [thick, color=uofgsandstone!50] (N1) -- (N4);
        \draw <2> [thick, color=uofgsandstone!50] (N2) -- (N4);
        \draw <2> [ultra thick] (N3) -- (N5);
        \draw <2> [ultra thick] (N3) -- (N6);
        \draw <2> [thick, color=uofgsandstone!50] (N4) -- (N6);
        \draw <2> [ultra thick] (N5) -- (N6);
        \draw <2> [thick, color=uofgsandstone!50] (N2) to [in=45, out=315] (N6);
        \draw <2> [thick, color=uofgsandstone!50] (N1) to [in=135, out=225] (N5);
    \end{tikzpicture}\end{center}

@@

    \begin{center}\begin{tikzpicture}
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (Na) at (1,  0) {1};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (Nb) at (1, -1.5) {2};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (Nc) at (0, -3) {3};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (Nd) at (2, -3) {4};

        \node <2> [draw, circle, fill=uofgcobalt, inner sep=4pt, font=\bfseries] (Na) at (1,  0) {1};
        \node <2> [draw, circle, fill=uofgpumpkin, inner sep=4pt, font=\bfseries] (Nb) at (1, -1.5) {2};
        \node <2> [draw, circle, fill=uofglawn, inner sep=4pt, font=\bfseries] (Nc) at (0, -3) {3};
        \node <2> [draw, circle, fill=uofgthistle, inner sep=4pt, font=\bfseries] (Nd) at (2, -3) {4};

        \draw <1> [thick, color=uofgsandstone!50] (Na) -- (Nb);
        \draw <1> [thick, color=uofgsandstone!50] (Nb) -- (Nc);
        \draw <1> [thick, color=uofgsandstone!50] (Nc) -- (Nd);
        \draw <1> [thick, color=uofgsandstone!50] (Nb) -- (Nd);

        \draw <2> [ultra thick] (Na) -- (Nb);
        \draw <2> [ultra thick] (Nb) -- (Nc);
        \draw <2> [ultra thick] (Nc) -- (Nd);
        \draw <2> [ultra thick] (Nb) -- (Nd);

        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N1) at (5.5,  0) {1};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N2) at (7.5,  0) {2};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N3) at (5.5, -1.5) {3};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N4) at (7.5, -1.5) {4};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N5) at (5.5, -3) {5};
        \node <1> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N6) at (7.5, -3) {6};

        \node <2> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N1) at (5.5,  0) {1};
        \node <2> [draw, circle, fill=uofgcobalt, inner sep=4pt, font=\bfseries] (N2) at (7.5,  0) {2};
        \node <2> [draw, circle, fill=uofgthistle, inner sep=4pt, font=\bfseries] (N3) at (5.5, -1.5) {3};
        \node <2> [draw, circle, fill=white, inner sep=4pt, font=\bfseries] (N4) at (7.5, -1.5) {4};
        \node <2> [draw, circle, fill=uofglawn, inner sep=4pt, font=\bfseries] (N5) at (5.5, -3) {5};
        \node <2> [draw, circle, fill=uofgpumpkin, inner sep=4pt, font=\bfseries] (N6) at (7.5, -3) {6};

        \draw <1> [thick, color=uofgsandstone!50] (N1) -- (N2);
        \draw <1> [thick, color=uofgsandstone!50] (N1) -- (N3);
        \draw <1> [thick, color=uofgsandstone!50] (N1) -- (N4);
        \draw <1> [thick, color=uofgsandstone!50] (N2) -- (N4);
        \draw <1> [thick, color=uofgsandstone!50] (N3) -- (N5);
        \draw <1> [thick, color=uofgsandstone!50] (N3) -- (N6);
        \draw <1> [thick, color=uofgsandstone!50] (N4) -- (N6);
        \draw <1> [thick, color=uofgsandstone!50] (N5) -- (N6);
        \draw <1> [thick, color=uofgsandstone!50] (N2) to [in=45, out=315] (N6);
        \draw <1> [thick, color=uofgsandstone!50] (N1) to [in=135, out=225] (N5);

        \draw <2> [thick, color=uofgsandstone!50] (N1) -- (N2);
        \draw <2> [thick, color=uofgsandstone!50] (N1) -- (N3);
        \draw <2> [thick, color=uofgsandstone!50] (N1) -- (N4);
        \draw <2> [thick, color=uofgsandstone!50] (N2) -- (N4);
        \draw <2> [ultra thick] (N3) -- (N5);
        \draw <2> [ultra thick] (N3) -- (N6);
        \draw <2> [thick, color=uofgsandstone!50] (N4) -- (N6);
        \draw <2> [ultra thick] (N5) -- (N6);
        \draw <2> [ultra thick] (N2) to [in=45, out=315] (N6);
        \draw <2> [thick, color=uofgsandstone!50] (N1) to [in=135, out=225] (N5);
    \end{tikzpicture}\end{center}
\end{frame}

@@

\begin{frame}{What About Induced?}

@@

    \only<5>{
        \input{gen-graph-induced-2d-5}
    }
\end{frame}

\begin{frame}[plain,t]{Induced in 3D?}

    \only<1>{
        \input{gen-graph-induced-3d-1}
    }

    \only<2>{
        \input{gen-graph-induced-3d-2}
    }

@@

    \only<6>{
        \input{gen-graph-shape-6}
    }
